When Risk Hits the Road: Does Danger Drive a Return?

### 2024-12-03 paper/paper.qmd
changes color of the predictor variable plots

# Create the plot
ggplot() +
  # Add basemap
  geom_sf(data = toronto_map$osm_polygons, fill = "gray90", color = "gray70") +
  # Add collision points with classification
  geom_sf(data = collision_data, aes(color = is_top_15), size = 0.5, alpha = 0.6) +
  scale_color_manual(values = c("High Collision Risk Neighborhoods" = "red", "Others" = "yellow")) +
  labs(
    x = "Longitude",
    y = "Latitude",
    color = "Neighborhood Type",
    title = "Neighborhood Collision Points in Toronto"
  ) +
  theme_minimal()

>>>>

# Create the plot
ggplot() +
  # Add basemap
  geom_sf(data = toronto_map$osm_polygons, fill = "gray90", color = "gray70") +
  # Add collision points with classification
  geom_sf(data = collision_data, aes(color = is_top_15), size = 0.5, alpha = 0.6) +
  scale_color_manual(values = c("High Collision Risk Neighborhoods" = "red", "Others" = "yellow")) +
  labs(
    x = "Longitude",
    y = "Latitude",
    color = "Neighborhood Type"
  ) +
  theme_minimal()
